Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-07-12 ms.tex
Updates from ShareLaTeX
started updating references in the parameter table to tie each number with a specific reference.
incorporated both Johanna's and Theodora's suggestions.

Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows the measurement of cloud vertical structure and composition, as gray grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity. The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A}, and amplitude spectra have been shown to vary with effective temperature, ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
Wavelength-dependent phase variations in lightcurves has also been observed \citep{2012ApJ...760L..31B,2013ApJ...778L..10B,2016ApJ...826....8Y}.
Since different wavelengths sample different photospheric depths in the highly structured spectra of L and T dwarfs, these phase variations have been interpreted as arising from the relative motion of distinct cloud layers or deep thermal pulsation \citep{2014ApJ...785..158R}.

@@

\begin{deluxetable*}{lllccccccccl}
\tablecaption{Brown Dwarf Properties}\label{tab:bdProp}
\tablewidth{0pt}
\tabletypesize{\footnotesize}
\tablehead{
\colhead{Name} & 
\multicolumn{2}{c}{Spectral Type} & 
\colhead{$d$} & 
\colhead{2MASS $H$} & 
\colhead{$J-K_s$} & 
\colhead{\lbol} & 
\colhead{\teff} & 
\colhead{P$_{rot}$} &
\colhead{$v\sin{i}$} & 
\colhead{$i$\tablenotemark{a}} & 
\colhead{Refs} \\
 &  \colhead{Opt} & \colhead{NIR} &  \colhead{(pc)} & &  & &  \colhead{(K)} & \colhead{(hr)} & \colhead{(km/s)} & \colhead{($\degr$)} \\
 }
\startdata
\sha\ & L5 & L7 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & $-$4.05$\pm$0.08 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 21 & 1-5 \\
\shb\ & L4.5p & L5 & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & $-$4.18$\pm$0.03 & 1635$\pm$66 & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 76 & 5-11 \\
\enddata
\tablenotetext{a}{Estimated inclination angle $i$ assuming a radius = 1 Jupiter radius, so that $\sin{i}$ = 8.0$\times$10$^{-3}Pv\sin{i}$, where $P$ is in hours and $v\sin{i}$ is in km/s. A value of $i$ $\approx$ 0{\degree} is viewed pole-on, $i$ $\approx$ 90{\degree} is viewed equator-on.}
\tablenotetext{b}{Tentative period.}
\tablerefs{(1) \citet{2003AJ....126.2421C};
(2) \citet{2016AJ....152...24W}; 
(3) \citet{2015ApJ...810..158F};
(4) \citet{2004MNRAS.354..378K};
(5) \citet{2010ApJ...723..684B};
(6) \citet{2008ApJ...686..528L}; 
(7) \citet{2016MNRAS.455..357S};
(8) \cite{2016ApJS..225...10F};
(9) \citet{2015ApJ...798...73G};
(10) \citet{2015ApJ...799..154M}
(11) \citet{2015ApJ...798L..13Y}; 
}
\end{deluxetable*}

@@

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{specphot_j0835.pdf}
	\label{fig:specphot0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
	\label{fig:specphot1821}
	}
	\caption{Top Panels: Normalized median raw spectra of {\sha} (left) and {\shb} (right) in black, compared with the respective reference stars (blue) and background emission (red; mostly telluric OH emission and thermal background).  Bottom Panels: Dynamic spectra of each brown dwarf system. The dynamic spectrum for \sha\ shows no significant variability in the spatial or spectral direction whereas \shb\ shows significant repeated modulations with a period near 4 hours.
The variability in \shb\ is prominent at the short wavelengths with a magnitude of ~$\sim$2\% peak-to-trough at short wavelengths but $\lesssim 0.5\%$ toward 2~$\mu$m.}
	\label{fig:specphot}
	\vspace{0.1in}
\end{figure*}

@@

\citet{hiranaka2016subMicronDust} find that the observed spectra of reddened L dwarfs can be explained by extinction from a haze layer of sub-micron forsterite grains.
They find typical mean particle radii of 0.15 to 0.35 $\mu$m for a sample of L dwarf stars.
Our median particle radius of $r$=0.24 $^{+0.05}_{-0.07}$~$\mu$m for \shb\ is consistent with this range and may represent a partially cloudy version of the reddened stars in \citet{hiranaka2016subMicronDust} or WISEP J0047+6803.

@@

2MASS J1821 shows significant variability up to the 1.5\% amplitude (3.0\% peak-to-valley) at short wavelengths (0.9~$\mu$m) which decreases towards the near infrared (2.4$~\mu$m).
This is consistent with HST measurements for the system that show a gradual decrease in variability amplitude with wavelength \citep{2016ApJ...826....8Y} from 1.1~$\mu$m to 1.7 $\mu$m with no decrease in the water vapor band.
The lack of the variability in the water vapor bands gives evidence of a high altitude aerosol layer in the atmosphere.
We find no statistically significant phase offsets in the light curves for \sha\ nor \shb\ from wavelength to wavelength.

>>>>

Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows the measurement of cloud vertical structure and composition, as gray grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity. The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A}, and amplitude spectra have been shown to vary with effective temperature, ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
Wavelength-dependent phase variations in lightcurves have also been observed \citep{2012ApJ...760L..31B,2013ApJ...778L..10B,2016ApJ...826....8Y}.
Since different wavelengths sample different photospheric depths in the highly structured spectra of L and T dwarfs, these phase variations have been interpreted as arising from the relative motion of distinct cloud layers or deep thermal pulsations. Deep thermal pulsations occur on longer timescales ($\sim$ 100 hr for an example T-dwarf model) but may interact wiht clouds to produce shorter timescale variability \citep{2014ApJ...785..158R}.

@@

\begin{deluxetable*}{lllllllllll}
\tablecaption{Brown Dwarf Properties}\label{tab:bdProp}
\tablewidth{0pt}
\tabletypesize{\footnotesize}
\tablehead{
\colhead{Name} & 
\multicolumn{2}{c}{Spectral Type} & 
\colhead{$d$} & 
\colhead{2MASS $H$} & 
\colhead{$J-K_s$} & 
\colhead{\lbol} & 
\colhead{\teff} & 
\colhead{P$_{rot}$} &
\colhead{$v\sin{i}$} & 
\colhead{$i$\tablenotemark{a}} \\
 &  \colhead{Opt} & \colhead{NIR\tablenotemark{a}} &  \colhead{(pc)} & &  & &  \colhead{(K)} & \colhead{(hr)} & \colhead{(km/s)} & \colhead{($\degr$)} \\
 }
\startdata
\sha\ & L5$^{(1)}$ & L7 & 7.27$\pm$0.02$^{(2)}$ & 11.94$\pm$0.02 & 2.03$\pm$0.03 & $-$4.05$\pm$0.08$^{(3)}$ & 1754$\pm$112$^{(3)}$ & 3.1\tablenotemark{b}$^{(4)}$ & 14.18$\pm$0.43$^{(5)}$ & 21 \\
\shb\ & L4.5p$^{(6)}$ & L5 & 9.38$\pm$0.03$^{(7)}$ & 12.40$\pm$0.02 & 1.78$\pm$0.03 & $-$4.18$\pm$0.03$^{(8)}$ & 1635$\pm$66$^{(8)}$ & 4.2$\pm$0.1$^{(9)}$ & 28.85$\pm$0.16$^{(5)}$ & 76 \\
\enddata
\tablenotetext{a}{This Work.}
\tablenotetext{b}{Estimated inclination angle $i$ assuming a radius = 1 Jupiter radius, so that $\sin{i}$ = 8.0$\times$10$^{-3}Pv\sin{i}$, where $P$ is in hours and $v\sin{i}$ is in km/s. A value of $i$ $\approx$ 0{\degree} is viewed pole-on, $i$ $\approx$ 90{\degree} is viewed equator-on.}
\tablenotetext{c}{Tentative period.}
\tablerefs{(1) \citet{2003AJ....126.2421C};
(2) \citet{2016AJ....152...24W}; 
(3) \citet{2015ApJ...810..158F};
(4) \citet{2004MNRAS.354..378K};
(5) \citet{2010ApJ...723..684B};
(6) \citet{2008ApJ...686..528L}; 
(7) \citet{2016MNRAS.455..357S};
(8) \cite{2016ApJS..225...10F} with updated values as discussed in Section \ref{sec:targets};
(9) \citet{2015ApJ...799..154M}
}
\end{deluxetable*}

@@

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{specphot_j0835.pdf}
	\label{fig:specphot0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
	\label{fig:specphot1821}
	}
	\caption{Top Panels: Normalized median raw spectra of {\sha} (left) and {\shb} (right) in black, compared with the respective reference stars (blue) and background emission (red; mostly telluric OH emission and thermal background). The areas of higher telluric absorption are visible near 1.4~$\mu$m and 1.8~$\mu$m.  Bottom Panels: Dynamic spectra of each brown dwarf system. The dynamic spectrum for \sha\ shows no significant variability in the spatial or spectral direction whereas \shb\ shows significant repeated modulations with a period near 4 hours.
The variability in \shb\ is prominent at the short wavelengths with a magnitude of ~$\sim$2\% peak-to-trough at short wavelengths but $\lesssim 0.5\%$ toward 2~$\mu$m.}
	\label{fig:specphot}
	\vspace{0.1in}
\end{figure*}

@@

\citet{hiranaka2016subMicronDust} find that the observed spectra of reddened L dwarfs can be explained by extinction from a haze layer of sub-micron forsterite grains.
They find typical mean particle radii of 0.15 to 0.35 $\mu$m for a sample of L dwarf stars.
Our median particle radius of $r$=0.24 $^{+0.05}_{-0.07}$~$\mu$m for \shb\ is consistent with this range and may represent a partially cloudy version of the reddened brown dwarfs in \citet{hiranaka2016subMicronDust} or WISEP J0047+6803.

@@

2MASS J1821 shows significant variability up to the 1.5\% amplitude (3.0\% peak-to-valley) at short wavelengths (0.9~$\mu$m) which decreases towards the near infrared (2.4$~\mu$m).
This is consistent with HST measurements for the system that show a gradual decrease in variability amplitude with wavelength \citep{2016ApJ...826....8Y} from 1.1~$\mu$m to 1.7 $\mu$m with no decrease in the water vapor band.
The lack of the variability in the water vapor bands gives evidence of a high altitude aerosol layer in the atmosphere.
We find no statistically significant phase offsets in the light curves for \sha\ nor \shb\ from wavelength to wavelength.
This is different from  \citep{2016ApJ...826....8Y} who found a significant phase offset using simultaneous Spitzer and HST light curves at two different epochs.
This may be due to the different pressures probed by the Spitzer Channel's 1 and 2 (3.6 $\mu$m and 4.5 $\mu$m) not found in our wavelength range.
